\begin{thebibliography}{20}
\bibitem{usage_stats_api}
\textit{API Usage Stats}
\\Dokumentacja Android
\\\texttt{https://developer.android.com/reference/android/app/usage/UsageStats}

\bibitem{publish_app}
\textit{Publikacja Aplikacji}
\\Dokumentacja Android
\\\texttt{https://developer.android.com/studio/publish}

\bibitem{discretization}
\textit{Global discretization of continuous attributes as preprocessing for machine learning}
\\Michal R. Chmielewski and Jerzy W. Grzymala-Busse, 01.11.1996
\\\texttt{
International Journal of Approximate Reasoning, Department of Electrical Engineering and Computer Science University of Kansas, Lawrence, Kansas, USA
}

\bibitem{weights}
\textit{Use and interpretation of logistic regression in habitat‐selection studies}
\\KEATING, K.A. and CHERRY, S., 2004
\\\texttt{The Journal of Wildlife Management, 68: 774-789. doi:10.2193/0022-541X(2004)068[0774:UAIOLR]2.0.CO;2 }

\bibitem{kotlinvsjava}
\textit{Kotlin – The unrivalled android
programming language lineage}
\\Manish Jangid, 2017
\\\texttt{Imperial Journal of Interdisciplinary Research (IJIR) Vol-3, Issue-8, 2017 ISSN: 2454-1362}

\bibitem{restapi}
\textit{Design and Describe REST API without Violating REST: A Petri Net Based Approach}
\\Li Li, Wu Chou 2011
\\\texttt{IEEE International Conference on Web Services, DOI: 10.1109/ICWS.2011.54 Washington, DC, USA}

\bibitem{crossvalid}
\textit{Sensitivity Analysis of k-Fold Cross Validation in Prediction Error Estimation}
\\Juan D. Rodriguez, Aritz Perez, Jose A. Lozano 03.2010
\\\texttt{IEEE Transactions on Pattern Analysis and Machine Intelligence Volume: 32, Issue: 3, DOI: 10.1109/TPAMI.2009.187}

\bibitem{aucvsacc}
\textit{Using AUC and accuracy in evaluating learning algorithms}
\\Jin Huang, C.X. Ling 03.2005
\\\texttt{IEEE Transactions on Knowledge and Data Engineering Volume: 17, Issue: 3, DOI: 10.1109/TKDE.2005.50}

\bibitem{auth_api}
\textit{API Google Auth}
\\Dokumentacja Google
\\\texttt{https://developers.google.com/android/reference/com/google/android/gms/auth}

\bibitem{reludeep}
\textit{Analysis of function of rectified linear unit used in deep learning}
\\Kazuyuki Hara, Daisuke Saito, Hayaru Shouno
\\\texttt{2015 International Joint Conference on Neural Networks (IJCNN) DOI: 10.1109/IJCNN.2015.7280578 Killarney, Ireland}

\bibitem{alarm_api}
\textit{API Alarm}
\\Dokumentacja Google
\\\texttt{https://developers.google.com/android/reference/com/google/android/gms/auth}

\bibitem{auc_roc}
\textit{Learning decision trees using the area under the ROC curve}
\\C. Ferri, P. Flach, and J. Hernandez-Orallo
\\\texttt{ICML-2002. Morgan Kaufmann, 2002}


\bibitem{ec2}
\textit{Deploying a Node App on Amazon EC2}
\\Kunal Yadav, 16 listopad 2018
\\\texttt{https://hackernoon.com/deploying-a-node-app-on-amazon-ec2-d2fb9a6757eb}

\bibitem{rescue_time}
\textit{Opis RescueTime}
\\Jory MacKay, 30 sierpień 2018
\\\texttt{https://blog.rescuetime.com/rescuetime-work-hours/}

\bibitem{quality_time}
\textit{Opis QualityTime}
\\Mobidays, Inc.
\\\texttt{https://www.qualitytimeapp.com/}



\bibitem{time_doctor}
\textit{Opis TimeDoctor}
\\TimeDoctor, 30 listopad 2019
\\\texttt{https://www.timedoctor.com/features.html}

\bibitem{logistic_regression}
\textit{An Introduction to Logistic Regression Analysis and Reporting}
\\Chao-Ying Joanne Peng, Kuk Lida Lee i Gary M. Ingersoll 
\\\texttt{2002, The Journal of Educational Research, 96:1, 3-14, DOI: 10.1080/00220670209598786}



\bibitem{one_hot_encoding}
\textit{High-Level Student Modeling with Machine Learning}
\\Gauthier G., Frasson C., VanLehn K
\\\texttt{2000 Intelligent Tutoring Systems. ITS 2000. Lecture Notes in Computer Science, vol 1839. Springer, Berlin, Heidelberg}


\bibitem{typeorm}
\textit{TypeORM - TypeScript guide}
\\David Herron, 18 lipiec 2019
\\\texttt{https://levelup.gitconnected.com/complete-guide-to-using-typeorm\\-and-typescript-for-data-persistence-in-node-js-module-bfce169959d9}

\bibitem{bayes}
\textit{Understanding probabilistic classifier}
\\Raedt, L. D., and Flach, P., Garg, A., and Roth, D. 2001.
\\\texttt{Proceedings of 12th European Conference on Machine Learning. Springer. 179–191.}


\bibitem{gini}
\textit{Introduction to Machine Learning and Data Mining}
\\Tue Herlau, Mikkel N. Schmidt and Morten Mørup, 31 styczeń 2019, pp. 156 - 157
\\\texttt{Technical University of Denmark}


\bibitem{knn}
\textit{A Study on Influence of Normalization Methods on Music Genre Classification Results Employing knn Algorithm}
\\Rosner Aldona, Michalak Marcin and Kostek B.
\\\texttt{2013. STUDIA INFORMATICA, vol. 34, no. 2A, pp. 411-423}

\bibitem{mlp}
\textit{When to Use MLP, CNN, and RNN Neural Networks}
\\Jason Brownlee, 23 lipiec 2018
\\\texttt{https://machinelearningmastery.com/when-to-use-mlp-cnn-and-rnn\\-neural-networks/}

\bibitem{cicd}
\textit{What is CI/CD? Continuous integration and continuous delivery explained}
\\Isaac Sacolick, 10 maj 2018
\\\texttt{https://www.infoworld.com/article/3271126/what-is-cicd-continuous\\-integration-and-continuous-delivery-explained.html}

\bibitem{interpr}
\textit{An introduction to variable and feature selection.}
\\I. Guyon, A. Elisseeff
\\\texttt{Journal of Machine Learning Research, 3(7-8):1157-1182, 2003.}

\bibitem{psqjson}
\textit{JSON Type}
\\The PostgreSQL Global Development Group, styczeń 2020
\\\texttt{https://www.postgresql.org/docs/9.2/datatype-json.html}




\end{thebibliography}